\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-06-26 exps.tex
little change

By utilizing in-house tools in conjunction with Worst-Case-Execution-Time (WCET)
analyzer \cite{jop:jnl:jsa2007} provided by JOP tools, we were able to estimate
BCRT and WCRT of the following benchmark programs: (full-name?) HRTCS \cite{},
Stepper motor controller (Motor) \cite{}, Robot and Access Environment Control
System (AECS) \cite{}. We have also added a set of customized hardware counters
to the original JOP design in order to collect clock cycles required for each
logical tick of given SystemJ program. All examples except Robot are existing
applications translated into pure SystemJ programs. The Robot example models a
combination of robotic arms and conveyors which splits goods based on their
volumetric sizes.

>>>>

By utilizing in-house tools in conjunction with Worst-Case-Execution-Time (WCET)
analyzer \cite{jop:jnl:jsa2007} provided by JOP tools, we were able to estimate
BCRT and WCRT of the following benchmark programs: (full-name?) HRTCS \cite{},
Stepper motor controller (Motor) \cite{}, Robot and Access Environment Control
System (AECS) \cite{}. We have also added a set of customized hardware counters
to the original JOP design in order to collect numbers of clock cycles required for 
logical ticks of given SystemJ program. All examples except Robot are existing
applications translated into pure SystemJ programs. The Robot example models a
combination of robotic arms and conveyors which splits goods based on their
volumetric sizes.
